\documentclass[a4paper,10pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0.1,0.3,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}

\titleformat{\subsection}{\large\scshape\raggedright}{}{0em}{}
\titlespacing{\subsection}{0pt}{0pt}{0pt}
%Tweak a bit the top margin
\addtolength{\voffset}{-1.3cm}

%Fixed-width right-aligned column
\usepackage{array}
\newcolumntype{x}[1]{%
>{\raggedleft\hspace{0pt}}p{#1}}%

%Pretty links
\newcommand{\schref}[2]{\href{#1}{\textsc{#2}}}
\newcommand{\mhref}[1]{\href{mailto:#1}{#1}}
\newcommand{\hhref}[1]{\href{http://#1}{#1}}

%Pretty tables
\newenvironment{cvtable}{\begin{tabular}{x{2cm}|p{11.6cm}}}{\end{tabular}}
\newcommand{\rowhead}[1]{\textsc{#1} &}
\newcommand{\rowdetail}[1]{& \footnotesize{#1}}

%Section references
\newcommand{\details}[1]{\hfill \hyperlink{details:#1}{\footnotesize Details}}
\newcommand{\detail}[2]{\hypertarget{details:#1}{\subsection{#2}}}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}
\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------HEADER-------------
\par{\centering
		{\Huge Michael \textsc{Walker}
	}\bigskip\par}

{\centering
5 Wilsthorpe Grove, York, North Yorkshire, England, YO10 4HU\\
\hhref{www.barrucadu.co.uk} \mhref{mike@barrucadu.co.uk}\\
(+44) (0) 7966875255\\
GPG: 9F58FC68\\
}

%--------------------SECTIONS-----------------------------------
\section{Work Experience}
\begin{cvtable}
  \rowhead{July 2012} Work experience at \schref{http://cs.york.ac.uk}{Department of Computer Science, University of York} \\
  \rowdetail{Use and analysis of data-mining tools.} \\

  \rowhead{August 2010} Work experience at \schref{http://www.arrivaldesign.co.uk/}{Arrival Design} \\
  \rowdetail{Website development in PHP and XHTML, including migration of code from ASP to PHP.}
\end{cvtable}

\section{Free Software Contributions}
\begin{cvtable}
  \rowhead{2010+} Project Leader, \schref{http://www.archhurd.org}{Arch Hurd}\\
  \rowdetail{Website and server maintenance, managing development team, compiling and maintaining software, producing installation media.}\\

  \rowhead{2009+} Web Developer, \schref{http://www.uzbl.org}{Uzbl}\\
  \rowdetail{Maintenance of website. Additionally, the website runs on a VPS I maintain.}\\

  \rowhead{2009+} Web Developer, \schref{http://www.gnu.org}{GNU Project}\\
  \rowdetail{Resolution of website issues as they arise, as part of a team of other maintainers.}\\

  \rowhead{2009}  Developer, \schref{http://www.uzbl.org}{Uzbl}\\
  \rowdetail{Implementation of various early functionality in a small development team, using C and Git.}
\end{cvtable}

\section{Education}
\begin{cvtable}
  \rowhead{2010+}       MEng (Computer Science), \textbf{University of York}, UK\\
  \rowdetail{Ongoing, due to graduate in 2014.} \details{csyork}\\

  \rowhead{2008--2010} A Levels, \textbf{Hymers College}, UK\\
  \rowdetail{Achieved grade A in Further Mathematics, Mathematics, and Physics. Achieved grade C in ICT.}\\

  \rowhead{2008--2010} AS Levels, \textbf{Hymers College}, UK\\
  \rowdetail{Achieved grade A in Computing. Achieved grade C in Psychology.}
\end{cvtable}

\section{Publications and Presentations}
\begin{cvtable}
  \rowhead{Feb 2013} Holistic Mathematics: An Exploration into Category Theory at \schref{http://mathsoc.cms.gre.ac.uk/tmt/}{TMT 2013}\\
  \rowdetail{An introduction to category theory and its applications given with Stijn S. C. Hanson.}
\end{cvtable}

\section{Computer Skills}
\begin{cvtable}
  \rowhead{Basic}       Autotools, Apache, Javascript, jQuery, ML, Scheme, Subversion\\
  \rowhead{Familiar}    Bash, CSS, Haskell, Java, {\fb\LaTeX}, Git, Microsoft Windows, MySQL, nginx, SQL\\
  \rowhead{Experienced} C, GNU/Linux, GNU/Hurd, PHP, Python, XHTML, Zsh
\end{cvtable}

\section{References}
\begin{tabular}{c}
  Dr Dimitar Kazakov\\
  Academic supervisor\\
  \mhref{kazakov@cs.york.ac.uk}\\
\end{tabular}

\section{Interests}
Free and Open Source Software, Programming Languages, Operating Systems, Computer Architectures, Mathematical Foundations of Computer Science, 19th and 20th Century Literature, Abstract Strategy Games, Japanese Culture, Kendo

\section{Details}

\detail{csyork}{MEng (Computer Science), University of York, UK}
\begin{tabular}{p{11cm}|c|c}
  \hline
  \textsc{Module Title}                        & \textsc{Result} & \textsc{Credit}\\

  \hline \multicolumn{3}{c}{\textbf{First Year}} \\ \hline
  Human Aspects of Computer Science            & 66\%            & 20\\
  Introduction to Computer Architectures       & 57\%            & 15\\
  Mathematical Foundations of Computer Science & 81\%            & 20\\
  Theory \& Practice of Programming            & 87\%            & 20\\
  Skills, Knowledge \& Independent Learning    & 100\%           & 5\\
  Digital Architecture Circuits \& Systems     & 51\%            & 30\\
  Numerical Analysis                           & 75\%            & 10\\
  \hline \textit{Overall Result}               & 83\%            & 120\\

  \hline \multicolumn{3}{c}{\textbf{Second Year}} \\ \hline
  Principles of Programming Languages          & 76\%            & 20\\
  Systems Software \& Compilers                & 59\%            & 30\\
  Software Engineering Project                 & 69\%            & 30\\
  Artificial Intelligence                      & 51\%            & 20\\
  Computability \& Complexity                  & 61\%            & 10\\
  Vision \& Graphics                           & 46\%            & 10\\
  \hline \textit{Overall Result}               & 74\%            & 120\\
  \hline
\end{tabular}

\end{document}
